---
title: "homework 6"
author: "Enbo Tian"
date: "2020/12/3"
output: pdf_document
---

## Problem 1
\begin{enumerate}
\item[(a)]
\end{enumerate}
```{r}
library(lubridate)
Rday<-read.csv("DailyLogRet-intc9608.txt",sep = "",skip = 2)
day <- ymd(Rday$date)
a = 1

Rmon <- rep(0,156)
count <- rep(0,156)
for(i in 1996:2008 ){
 for(j in 1:12){
   data = 0
   n =0
    for(k in 1:3274){
      if(year(day[k])==i & month(day[k])==j){
        data = data+Rday$rtn[k]
        n = n+1
      }
      Rmon[a] = data
      count[a] = n
    }
    a = a+1
  }
}
Rmon
```
\begin{enumerate}
\item[(b)]
\end{enumerate}
```{r}
#find the ACF value at lag 1
acf(Rday$rtn,lag.max =1, plot = F)

r1 =-0.044
vart <- rep(0,156)
a = 1
for(i in 1: 156){
  sum = 0
  for( j in 1: count[i]){
    sum = sum+(Rday$rtn[a]-Rmon[i]/count[i])^2
    a =a +1
  }
  
  vart[i] <- (1+ 2*r1)/(count[i]-1)*sum
}
 vart
```

\begin{enumerate}
\item[(c)]
\end{enumerate}
```{r}
summary(Rday$rtn) # day summary
summary(Rmon) # month summary
```

\begin{enumerate}
\item[(d)]
\end{enumerate}
```{r}
lnvart <- log(vart)
summary(vart)
summary(lnvart)
## N = 156 for var and ln var
```
\begin{enumerate}
\item[(e)]
\end{enumerate}
```{r}
library(TSA)
eacf(lnvart, ar.max = 10, ma.max = 10)
est <- arima(lnvart, order=c(13,0,1), include.mean = T)
est
```

```{r}
T = length(lnvart)
(pmax = floor(12 * (T/100)^(1/4)))

estt = (0.9553-1)/0.028

estlnvart <- rep(0,142)
for (t in 15: 156){
  sum = 0
  for(i in 1:pmax){
    sum=sum+0.9553*(lnvart[t-i]-lnvart[t-i-1])
  }
 estlnvart[t-14] = -0.7596+(0.9553-1)*lnvart[t-1]+sum+est$residuals[t]
}
estlnvart
```

## Problem 2
\begin{enumerate}
\item[(a)]
\end{enumerate}
```{r}
unem<-read.csv("m-unrate.txt",sep = "")
unts <- ts(unem$Rate, start=c(1948,1), freq = 12)
plot(unts, ylab='rate') #ts plot
summary(unts) #summary
acf(unts) # acf plot
pacf(unts)# pacf plot
eacf(unts, ar.max = 10, ma.max = 10)
```
\begin{enumerate}
\item[(b)]
\end{enumerate}
```{r}
est1 <-arima(unts, order=c(2,0,2), include.mean = T)
est2 <-arima(unts, order=c(3,0,2), include.mean = T)#ARMA(3,2) perfered
est3 <-arima(unts, order=c(2,0,3), include.mean = T)
est1
est2
est3
Box.test(est1$residuals, lag = 13, type = "Ljung-Box", fitdf=2+2)
Box.test(est2$residuals, lag = 13, type = "Ljung-Box", fitdf=2+3)
Box.test(est3$residuals, lag = 13, type = "Ljung-Box", fitdf=3+2)
```
\begin{enumerate}
\item[(c)]
\end{enumerate}
```{r}
pred.dat <- predict(est2, n.ahead=4)
pred.dat
```

\begin{enumerate}
\item[(d)]
yes, since he AR polynomial relate to the behavior of stochastic cycles.

\item[(e)]
\end{enumerate}
```{r}
library(FinTS)
dif12 = diff(unts, lag=12)
dif = diff(unts); ddif12 = diff(dif, lag=12)
fit <- ARIMA(dif, order=c(3,0,2),seasonal=list(order=c(0,0,2), period=6), Box.test.lag=15)
fit$Box.test

## the corresponding period is 6
```

## Problem 3
```{r}
ele<-read.csv("power6.txt")
elets <- ts(ele$power)
plot(elets, ylab='logpower') 
summary(elets)
eacf(elets, ar.max = 10, ma.max = 10)
est <-arima(unts, order=c(2,0,2), include.mean = T)
est
Box.test(est$residuals, lag = 13, type = "Ljung-Box", fitdf=2+2)
fit <- ARIMA(dif, order=c(2,0,2),seasonal=list(order=c(0,1,1), period=11), Box.test.lag=14)
fit$Box.test

```