---
title: "problem 4"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Problem 4  
The file `MortBond.txt' contains monthly effective interest rate $z_t$  for conventional single- family mortgages from Jan. 1973 to Dec. 2003. 
```{r}
Mort = read.csv("MortBond.txt",head = T, sep="");
mortrate = ts(Mort[,2],start = 1937,freq =12);

```

\begin{enumerate}

	\item[(a)] Draw threes plots: time plot of the time series, scatter plots of $z_{t+1}$ versus $z_t$ and of $z_{t+2}$ versus $z_t$.
\end{enumerate}	
```{r}
##-- second column is monthly interest rate for conventional single-family mortgage.
Mort = read.csv("MortBond.txt",head = T, sep="");
mortrate = ts(Mort[,2],start = 1937,freq =12);
ts.plot(mortrate,gpars = list(xlab = "Month", ylab = "mortrate"),main = "time series")
z01 = tail(mortrate,-1)
z02 = tail(mortrate,-2)
z1 = head(mortrate,-1)
z2 = head(mortrate,-2)
plot(z1, z01, xlab = "z_t+1", ylab = "z_t")
plot(z2, z02, xlab = "z_t+2", ylab = "z_t")
```
\begin{enumerate}
\item[(b)] Based on the plots in (a), do you think that the series is autocorrelated? Comment on whether you think the time series is stationary.
	
	Since the scatter plot is linear, the series is autocorrelated
	
	Since the trend of the time series has a crest beyond 1980, it is not stationary.
	
	\item[(c)] Plot the sample autocorrelation for this series up to lag 40.  Relate this plot to the plots in (a).
	
\end{enumerate}
 
