---
title: "homework 3"
author: "Enbo Tian"
date: "2020/10/14"
output: pdf_document
---

## Problem 1
\begin{enumerate}
\item[]
Since $\gamma(k) = 0 $ for $k >2 $, it can apply to MA(2).

$ Y_t = \mu +\epsilon_t - \theta_1\epsilon_{t-1}- \theta_2\epsilon_{t-2}$

Since $\gamma(1) = 0 $, $ \sigma^2(-\theta_1+\theta_1\theta_2)= 0$, implys $-\theta_1+\theta_1\theta_2 = 0 $ then $\theta_2 =1$

$\sigma^2(-\theta_2)= -1.6$ implys $ \sigma^2 = 1.6$

$\sigma^2(1+ \theta_1^2+\theta_2^2) = 4 $

$ 1.6(1+\theta_1^2+1)=4$ 

$ \theta_1 = \frac{\sqrt{2}}{2}$

let $\mu =0 $, $Y_t=\epsilon_t-\frac{\sqrt{2}}{2}\epsilon_{t-1}-\epsilon_{t-2}$, $ \{\epsilon_t\}\sim WN(0,1.6)$

\end{enumerate}
## Problem 2
\begin{enumerate}
\item[(a)]
$ Y_t = \frac{1}{3}Y_{t-1}+\frac{2}{9}Y_{t-2}+\epsilon_t$, then $\phi_1 = \frac{1}{3}$ and $ \phi_2 =\frac{2}{9}$

the root of $1-1/3z-2/9z^2=0$are $z_1=-3$ and $z_2=3/2$, both$|z_1|,|z_2|>1$, then $\{Y_t\}$ is causal.

$\rho(1)= \frac{\phi_1}{1-\phi_2} = \frac{3}{7} =0.429$

$\rho(2)=\phi_1\rho(1)+ \phi_2\rho(0) = \frac{1}{3}\times0.429+\frac{2}{9}\times1=0.365$

$\rho(3)=\phi_1\rho(2)+ \phi_2\rho(1) = \frac{1}{3}\times0.365+\frac{2}{9}\times0.429=0.217$
\item[(b)]
\end{enumerate}

```{r}
# i
nlag =30
acf.ar2 = ARMAacf(ar=c(1/3,2/9), lag.max=nlag)
plot(0:nlag, acf.ar2, type="h",xlab="lag");

pacf.ar2 = ARMAacf(ar=c(1/3,2/9), lag.max=nlag,pacf = TRUE)
plot(0:29, pacf.ar2, type="h",xlab="lag");
#ii
par(mfrow=c(3,3))
for(i in 1:3){
  AR2 = arima.sim(list(order=c(2,0,0), ar=c(1/3,2/9)),n =100,sd=sqrt(2))
  ts.plot(AR2, main="AR(2) phi1=1/3 phi2=2/9,mu=10,sd=sqrt(2)")
  acf(AR2, lag.max=nlag)
  pacf(AR2, lag.max=nlag)
  abline(h=0)
}

# iii: these figures plot the therretical ACF and PACF to lag 30. There is a acf until lag 10, and pacf occur before lag 2.
# For three times simulate of 100 observations with ts plot, acf and pacf,  most of the acf and pacf are bounded in after lag 2.
```
\begin{enumerate}
\item[(c)]
By solveing the equation, $m_1 =\frac{2}{3}$ and $m_2=-\frac{1}{3}$
Since both $m_1,m_2 <1$ 

$\rho(k) = c_1*(\frac{2}{3})^k+ c_2*(-\frac{1}{3})^k$

apply to $\rho(0),\rho(1)$,$c_1+c_2=1$,$2/3c_1-1/3c_2=0.429$
$c_1=0.762 ,c_2=0.237 $

$\rho(k) = 0.762*(\frac{2}{3})^k+ 0.237*(-\frac{1}{3})^k$, $ k = 1,2....$
\end{enumerate}

## Problem 3
\begin{enumerate}
\item[(a)]

Since $1-1.3z+0.8z^2 = 0$ have the root $z= 13/16\pm i\sqrt{151}/16 \approx0.8+0.7i$,$|z_1|=|z_2|=1.11>1$ so the process is causal.

$\mu =E(Y_t)= 3.5/(1-1.3+0.8)=7$

$ \gamma(0) =Var(Y_t)= \frac{1+0.8}{1-0.8}\frac{3^2}{(1+0.8)^2-1.3^2}=52.2$

\item[(b)]

$ \rho(1) = \phi_1/(1-\phi_2)=1.3/(1+0.8) = 0.722$

$\rho(2) =\phi_1\rho(1) +\phi_2\rho(0) = 1.3*0.722+(-0.8)*1=0.139$

$ \rho(3) =1.3*0.139+(-0.8)*0.722 =-0.397$

$\rho(4) = 1.3*(-0.397)-0.8* 0.139=-0.6275$

$\rho(5) = 1.3*(-0.6275)-0.8*(-0.397)=-0.497$

\item[(c)]
$m^2-1.3m+0.8=0$

$m=0.65\pm0.614i$, $R=|m_1| =|m_2|=0.894 $

$cos(\lambda) = 0.65/0.894=0.727$, $\lambda = 0.757$

$\rho(k) = 0.894^k[c_1cos(0.757k)+c_2sin(0.757k)]$ 

apply to $\rho_0,\rho_1$, $c_1=1$, $c_2=0.117$
$\rho(k) = 0.894^k[cos(0.757k)+0.117sin(0.757k)]$,for $k = 0,1,2...$

$\rho(1) = 0.894[cos(0.757)+0.117sin(0.757)] =0.722$

$\rho(2) = 0.894^2[cos(0.757*2)+0.117sin(0.757*2)] =0.138$

$\rho(3) = 0.894^3[cos(0.757*3)+0.117sin(0.757*3)] =-0.397$

$\rho(4) = 0.894^4[cos(0.757*4)+0.117sin(0.757*4)] =-0.627$

$\rho(5) = 0.894^5[cos(0.757*5)+0.117sin(0.757*5)] =-0.497$
\item[(d)]
\end{enumerate}
```{r}
ARMAacf(c(1.3,-0.8),lag.max = 5)
```
\begin{enumerate}
\item[(e)]
$ \psi_0=1$

$ \psi_1=\phi_1\psi_0=1.3$

$ \psi_2=\phi_1\psi_1+\phi_2\psi_0=0.89$
$ \psi_3=\phi_1\psi_2+\phi_2\psi_1=0.917$
$ \psi_4=\phi_1\psi_3+\phi_2\psi_2=0.4801$
$ \psi_5=\phi_1\psi_4+\phi_2\psi_3=0.10947$
$ Y_t = 7 +\epsilon_t+1.3\epsilon_{t-1}+0.89\epsilon_{t-2}+0.917\epsilon_{t-3}+0.4801\epsilon_{t-4}+0.10947\epsilon_{t-5}$
\end{enumerate}

## Problem 4
\begin{enumerate}
\item[(a)]
For AR(1) model $ \gamma(1) = \phi\gamma(0) = \rho(1)\gamma(0)$

$ \phi = 0.8$

For AR(2) model 

$ \gamma(1) = \phi_1\gamma(0)+\phi_2\gamma(1)=\rho(1)\gamma(0)$

$ \gamma(2) = \phi_1\gamma(1)+\phi_2\gamma(0)=\rho(2)\gamma(0)$

$\phi_1 = 1.2 ,\phi_2= -0.5$

For AR(3) model 
$ \gamma(1) = \phi_1\gamma(0)+\phi_2\gamma(1)+\phi_3\gamma(2)=\rho(1)\gamma(0)$

$ \gamma(2) = \phi_1\gamma(1)+\phi_2\gamma(0)+\phi_3\gamma(1)=\rho(2)\gamma(0)$

$ \gamma(3) = \phi_1\gamma(2)+\phi_2\gamma(1)+\phi_3\gamma(0)=\rho(3)\gamma(0)$

$\phi_1 =1.2 ,\phi_2=-0.5,\phi_3=0$
\item[(b)]
For AR(1) model 
$\sigma^2 = \gamma(0)[1-\phi\rho(1)] = 2.16 $

For AR(2) model
$\sigma^2 = \gamma(0)[1-\phi_1\rho(1)-\phi_2\rho(2)] = 1.62 $

For AR(3) model
$\sigma^2 = \gamma(0)[1-\phi_1\rho(1)-\phi_2\rho(2)-\phi_3\rho(3)] = 1.62 $

\item[(c)]

Since $\phi_3 = 0$ This is a AR(2) process
\end{enumerate}

## Problem 5
\begin{enumerate}
\item[]

Since $m_1,m_2$ are root of $m^2-\phi_1m-\phi_2=0 $

$m_1,m_2 = \frac{\phi_1\pm\sqrt{\phi_1+4\phi_2}}{2}$

Then $m_1+m_2 = \phi_1$, and $m_1m_2 = -\phi_2 $

Since $m_1=x+iy$ and $m_2=x-iy $, $x = \frac{m_1+m_2}{2}$ and $m_1m_2=(x+iy)(x-iy)=x^2+y^2 $

$R = \sqrt{x^2+y^2} = \sqrt{m_1m_2} $

By the way
$cos(\lambda)=\frac{x}{R}=(\frac{m_1+m_2}{2})/\sqrt{m_1m_2} =\frac{m_1+m_2}{2\sqrt{m_1m_2}} = \frac{\phi_1}{2\sqrt{-\phi_2}} $

\end{enumerate}